\documentclass[11pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\usepackage{xcolor}

\usepackage{float}
\title{Public key cryptography in OpenSSl \\ HW6 - CNS Sapienza}

\author{Edoardo Puglisi 1649359} 
\date{12/12/2019}

\begin{document}
\lstset{breaklines=true}
	
\maketitle
\tableofcontents
\clearpage

\section{Overview}
The main purpose of this paper is to define the OpenSSL workflow for generating key-pairs and certificates, converting certificates and digital signing documents in particular using RSA and DSA.

\section{Generating keys}
In OpenSSL secret keys can be generated with $genpkey$ command. The use of it change according on the algorithm used. For RSA just set as parameters algorithm and output file:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl genpkey -algorithm RSA -out pkeyRSA.pem
\end{lstlisting}
Other key generation option can be set such as the number of bits of generated key (deafult 2048) or the public key exponent value.
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
-----BEGIN PRIVATE KEY-----
MIIEvgIBADANBgkqhkiG9w0BAQEFAASCBKgwggSkAgEAAoIBA...
-----END PRIVATE KEY-----
\end{lstlisting}
For DSA algorithm the procedure is a bit diffent. First we must define the set of parameters for the key generator:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl genpkey -genparam -algorithm DSA -out dsap.pem
\end{lstlisting}
then create the key from the previously generated parameters set.
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl genpkey -paramfile dsap.pem -out pkeyDSA.pem
\end{lstlisting}
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
-----BEGIN PRIVATE KEY-----
MIIBSgIBADCCASsGByqGSM44BAEwggEeAoGBAM...
-----END PRIVATE KEY-----
\end{lstlisting}
Given this new fileS we can extract the public keys:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl rsa -pubout -in pkeyRSA.pem -out pubRSA.pem
openssl dsa -pubout -in pkeyDSA.pem -out pubDSA.pem
\end{lstlisting}
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
-----BEGIN PUBLIC KEY-----
MIIBtzCCASsGByqGSM44BAEwggEeAoGBAM1kgabPEgZe0Ijj....
-----END PUBLIC KEY-----
\end{lstlisting}

\section{Generating and verifying X.509 certificate}
To generate a selfsigned certificate (X.509) we run the command:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl req -new -x509 -sha256 -days 365 -key pkeyRSA.pem -out certificate.crt
\end{lstlisting}
It takes as argument the validity and the private key we generated previously. You will be asked to insert certificate attributes such as location, organization name and common name.
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
Country Name (2 letter code) []:IT
State or Province Name (full name) []:Italy
Locality Name (eg, city) []:Roma
Organization Name (eg, company) []:Sapienza
Organizational Unit Name (eg, section) []:CNS
Common Name (eg, fully qualified host name) []:Diag
Email Address []:
\end{lstlisting}
To verify the self-signed certificate:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl verify -CAfile certificate.crt certificate.crt
------------
certificate.crt: OK
\end{lstlisting}

\section{Signing and verifying a document}
To sign a document use command $dgst$ as following:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl dgst -sign pkeyRSA.pem -out signature input.txt
\end{lstlisting}
This command compute the sha256 of the input file and sign it with the private key. To verify the document given the public key instead:
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl dgst -verify pubRSA.pem -signature signature input.txt 
------------
Verified OK
\end{lstlisting}

\section{Converting certificate formats}
The same command used to create a selfsigned X.509 certificate can be used to convert certificates in different formats.
\begin{lstlisting}[backgroundcolor = \color{lightgray}]
openssl x509 -in certificate.crt -out converted-certificate.der -outform DER
\end{lstlisting}
In this example the previously created certificated is converted in DER format.


\end{document}
